Andres Karjus

### 2021-01-12 news.Rmd
news

- Gave an invited talk about my PhD research on lexical dynamics at the [Colloquium for Computational Linguistics and Linguistics in Stuttgart](https://www.ims.uni-stuttgart.de/en/research/colloquium/). The [Slides](https://andreskarjus.github.io/talks/stuttgart2021/andres_karjus_lexical_dynamics_slides_stuttgart2021.pdf) | [Recording](https://www.ims.uni-stuttgart.de/documents/aktuelles/veranstaltungen/210111-Karjus-Talk-Colloq-Recording.mp4)

>>>>

- Gave an invited talk about my PhD research on lexical dynamics at the [Colloquium for Computational Linguistics and Linguistics in Stuttgart](https://www.ims.uni-stuttgart.de/en/research/colloquium/). (11.01.2021) [Slides](https://andreskarjus.github.io/talks/stuttgart2021/andres_karjus_lexical_dynamics_slides_stuttgart2021.pdf) | [Recording](https://www.ims.uni-stuttgart.de/documents/aktuelles/veranstaltungen/210111-Karjus-Talk-Colloq-Recording.mp4)
